Soss

### 2020-01-01 paper/paper.tex
edits

\begin{description}  
    \item[\texttt{rand}] draws a random sample from a given joint distribution 
    \item[\texttt{particles}] uses \emph{systematic sampling}
    \item[\texttt{logpdf}]
    \item[\texttt{symlogpdf}] 
    \item[\texttt{weightedSample}] 
    \item[\texttt{xform}] 
\end{description}

>>>>

\todo[inline]{citation for MonteCarloMeasurements.jl}

\begin{description}  
    \item[\texttt{rand}] draws a random sample from a given joint distribution.
    \item[\texttt{particles}] draws a \emph{systematic sample} from a given joint distribution, using \texttt{MonteCarloMeasurements.jl}.
    \item[\texttt{logpdf}] takes a joint distribution and a point in its sample space, and returns the log-density.
    \item[\texttt{symlogpdf}] 
    \item[\texttt{weightedSample}] 
    \item[\texttt{xform}] 
\end{description}
